Appendix S1: Supporting Tables and Figures

### 2022-04-28 ms/SI.Rmd
Print out SI tree fig to PDF first
fixes problem of jumbled text in tip labels

```{r tree, fig.width = 8, fig.height = 8}
phy <- japan_pterido_tree

@@

rotate_tree(p, 3)
```

>>>>

```{r tree_make}
phy <- japan_pterido_tree

@@

p_rot <- rotate_tree(p, 3)

tree_fig_file <- glue::glue("results/{s_figure('tree')}.pdf") %>%
  str_replace_all(" ", "_") %>%
  here::here()

ggsave(
 file = tree_fig_file, plot = p_rot, height = 7, width = 7, units = "in")
```

```{r, tree-print, fig.width = 7, fig.height = 7, results = "show"}
knitr::include_graphics(tree_fig_file)
```
